---
title: "DSC Demographics"
author: "John Curcio"
date: "March 17, 2018"
output: html_document
---

```{r}
dsc_df <- read.csv("dsc-demographics.csv")
head(dsc_df)
```

## Removing missing values

```{r}
sum(is.na(dsc_df$Class.Level)) 
sum(dsc_df$Class.Level[!is.na(dsc_df$Class.Level)] == "")
sum(dsc_df$Departments == "")
sum(dsc_df$Class.Level[!is.na(dsc_df$Class.Level)] == "" &
      dsc_df$Departments[!is.na(dsc_df$Class.Level)] == "")
```

When I actually google the names of people with `NA` in their class level, I find that they've got some kind of unusual CMU enrollment status to begin with. At any rate, it's no fault in my code.

```{r}
dsc_df[is.na(dsc_df$Class.Level),]
```

When I search for the names of people with empty strings in their class level and department, I find no matches in the directory. 

`mmrosenb` is, for example, a former DSC officer who graduated last year. His emails probably weren't bouncing because he's a manager for the group.

It's possible that these were just andrews that were incorrectly entered.

```{r}
dsc_df[dsc_df$Class.Level == "",]
```

Anyway, let's get rid of them all. We're looking at 375 members.

```{r}
active_dsc_df <- subset(dsc_df, !is.na(dsc_df$Class.Level) & (dsc_df$Departments != ""))
nrow(active_dsc_df)
head(active_dsc_df)
```

## Computing summary stats

```{r}
table(active_dsc_df$Class.Level) 

table(active_dsc_df$Class.Level) / 375
```

People can have more than one department, so `Departments` has a ton of levels.

```{r}
head(active_dsc_df$Departments)
```


```{r}
sum(grepl("Computer Science", active_dsc_df$Departments))
sum(grepl("Statistics", active_dsc_df$Departments))
sum(grepl("Engineering", active_dsc_df$Departments))
sum(grepl("Electrical &amp; Computer Engineering", active_dsc_df$Departments))
sum(grepl("Business", active_dsc_df$Departments))
sum(grepl("Mathematical Sciences", active_dsc_df$Departments))
```


The following 20 majors account for more than 75% of our members. The rest are double-majors or whatever.

Lots of people add Statistics as an additional major.

```{r}
dept_breakdown <- sort(table(active_dsc_df$Departments), decreasing = T)
sum(dept_breakdown[1:15])
dept_breakdown[1:15]
```

